---
title: "data_management_sqlite"
author: "Keenan Smith"
---

```{r}
here::i_am("content/data_management/data_management_sqlite.qmd")
```

# Library Load

```{r}
#| label: Library Load
library(DBI)
library(dplyr)
library(duckdb)
library(here)
```

# Connecting to the SQLite DB

```{r}
#| label: Connecting the Corpus DB
corpus_db <- dbConnect(RSQLite::SQLite(), here("data","corpus_db.sqlite"))
```

# Reading Original Corpus

This corpus contains all the viable article text and metadata for the original text corpus. This data includes Brookings Institute, Jacobin, American Mind, and the Heritage Foundation

```{r}
#| label: Reading in Original 4 source Corpus
original_corpus <- readr::read_rds(here("data", "text_full_corpus.rds"))
```

# Manipulating Original Corpus

Data needs to be manipulated so that it fits better into SQL data types

```{r}
#| label: Manipulating the Corpus to include data better for SQL
original_corpus_date_edited <- original_corpus |>
  mutate(year = lubridate::year(art_date),
         month = lubridate::month(art_date),
         day = lubridate::day(art_date)) |>
  select(-art_date) |>
  distinct(art_link, .keep_all = TRUE)
```

# Creating Table in SQLite

```{r}
#| label: Writing Original Corpus to New SQLite db
#| eval: false

# dbRemoveTable(corpus_db, "original_corpus")

# dbWriteTable(corpus_db, "original_corpus", original_corpus_date_edited)

# dbListTables(corpus_db)

# dbListFields(corpus_db, "original_corpus")
```

# Creating Unique Index on Link

```{r}
#| label: Creating Index on art_link
#| eval: false

# dbSendStatement(corpus_db, "CREATE UNIQUE INDEX art_link ON original_corpus (art_link)")
```

# Query Testing

```{r}
#| label: Testing new DB

dbGetQuery(corpus_db, "SELECT * FROM original_corpus LIMIT 10")
```

# Testing dbplyr

```{r}
original_corpus_db_test <- tbl(corpus_db, "original_corpus")
```

# DB Disconnect

```{r}
#| label: Disconnect Block
dbDisconnect(corpus_db)
```

