---
title: "Exploratory Data Analysis"
author: "Keenan Smith"
editor_options: 
  chunk_output_type: console
---

Built with R Version `r getRversion()`

```{r}
#| output: false
#| label: Reading in initial Libraries
here::i_am("content/exploratory_data_analysis/exploratory_data_analysis_quanteda.qmd")
library(tidytable)
library(ggplot2)
library(quanteda)
library(quanteda.textstats)
library(quanteda.textplots)
```

# START HERE

# Reading In already Processed Document Feature Matrices & Token Objects

```{r}
bigram_stopterms_post_write <- c("new_york", "american_progress", "en_el", "de_los", "de_la", "la_de", "en_las", "en_la", "de_las", "see_also", "right_right", "left_left", "getty_images", "world_week", "solely_author", "please_see", "topic_please", "senior_american", "associate_director", "team_american", "solely_expressed", "douglas_sarah", "roe_economic", "resident_american", "allison_foreign", "pdf_read", "opinions_expressed", "international_scholars", "sarah_allison", "thomas_roe", "never_ways", "emphasis_added", "article_published", "newsletter_never", "expressed_solely", "report_pdf", "michael_barone", "thatcher_freedom", "margaret_thatcher", "policy_team", "special_assistant", "see_graph", "read_full", "et_al", "one_two", "tell_us", "looks_like", "may_well", "may_also", "just_like", "tells_us", "full_report", "full_article", "bergman_group", "reflect_views", "asia_program")
```

## Words

```{r}
polsent_corpus <- readr::read_rds(here::here("data", "tokens", "corpus.rds"))

toks_polsent <- readr::read_rds(here::here("data", "tokens", "filtered_tokens.rds"))
dfmat_polsent <- readr::read_rds(here::here("data", "tokens", "dfmat_polsent.rds"))
```

```{r}
words_stopterms_from_bigrams <- unique(unlist(strsplit(bigram_stopterms_post_write, "_")))

word_trim <- dfm_remove(dfmat_polsent, pattern = words_stopterms_from_bigrams)

# Trimmed word Data for Frequency as well
dfmat_words_trim <- dfm_trim(dfmat_polsent, min_termfreq = 3000, termfreq_type = "rank")

# Grouping Words Based on Source Bias
dfmat_group <- dfmat_words_trim |>
  dfm_group(groups = source_bias)
```

## Bigrams

```{r}
# toks_polsent_bigrams <- readr::read_rds(here::here("data", "tokens", "filtered_bigrams.rds"))
dfmat_polsent_bigrams <- readr::read_rds(here::here("data", "tokens", "dfmat_polsent_bigrams.rds"))

bigram_trim <- dfm_remove(dfmat_polsent_bigrams, pattern = bigram_stopterms_post_write)

filtering <- topfeatures(bigram_trim, n = 4000) |> as.list() |> as_tidytable() |> pivot_longer()

specifics <- filtering |>
  filter(stringr::str_detect(name, "^pdf_"))

# Trimmed Frequency to Make Data Easier to Manage
dfmat_bigrams_trim <- dfm_trim(bigram_trim, min_termfreq = 4000, termfreq_type = "rank")

# Grouping Bigrams Based on Source Bias
dfmat_group_bigrams <- dfmat_bigrams_trim |>
  dfm_group(groups = source_bias)
```

# Using Quanteda to Analyze Data

## TF-IDF Vectorization of Individual Documents

USE FOR MODELING

```{r}
dfmat_bigrams_tfidf <- dfm_tfidf(dfmat_bigrams_trim)
```

# Tidied Group Data on Bias

CONVERT FOR MODELING

```{r}
convert_bigrams_bow <- convert(dfmat_bigrams_trim, to = "data.frame")
fwrite(convert_bigrams_bow, here::here("data", "model_data", "bow_bigram_df_4k.csv.gz"))
convert_bigrams_tfidf <- convert(dfmat_bigrams_tfidf, to = "data.frame")
fwrite(convert_bigrams_tfidf, here::here("data", "model_data", "tfidf_bigram_df_4k.csv.gz"))
```

## Frequency Analysis

RUN ONCE MODELS ARE COMPLETED

```{r}
tstat_bigram_freq <- textstat_frequency(dfmat_bigrams_trim, n = 200, groups = source_bias)
fwrite(tstat_bigram_freq, here::here("content", "project", "tstat_freq_bigram.csv"))

left_bigram_freq <- subset(tstat_bigram_freq, group == "left-wing")
right_bigram_freq <- subset(tstat_bigram_freq, group == "right-wing")
```

### Individual Bigram Frequency WordCloud

```{r}
wordcloud2::wordcloud2(left_bigram_freq, size = 1.5, color = pals::ocean.thermal(100), minRotation = pi/6, maxRotation = pi/6, rotateRatio = 1)
wordcloud2::wordcloud2(right_bigram_freq, size = 1.5, color = pals::ocean.oxy(100), minRotation = -pi/6, maxRotation = -pi/6, rotateRatio = 1)
```

```{r}
#| fig-width: 8
#| fig-height: 8
# create wordcloud
set.seed(132) # set seed for reproducibility
textplot_wordcloud(dfmat_group_bigrams, comparison = TRUE, max_words = 500,  color = c("red", "blue"))
```

## Grouping by Article Source

RUN IF WORDS CHANGE

```{r}
dfmat_group_source <- dfm_group(dfmat_words_trim, groups = short_source) |>
  dfm_select(min_nchar = 2)
```

## Lexical Diversity Between Sources

RUN IF WORDS CHANGE

```{r}
tstat_lexdiv <- textstat_lexdiv(dfmat_group_source)
tstat_lexdiv
```

```{r}
ggplot(tstat_lexdiv, aes(document, TTR)) + 
  geom_col(aes(fill = document)) +
  labs(x = "Article Sources",
       y = "Lexical Diversity") +
  ggthemes::theme_clean() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
        legend.position = "none")

ggsave(here::here("content", "project", "images", "art_source_lexical_diversity.png"))
```


## Collocation on Tokens

RUN IF TOKENS CHANGE

[Source for How to Do This](https://tutorials.quanteda.io/statistical-analysis/collocation/)

```{r}
tstat_col_caps <- tokens_select(toks_polsent, pattern = "^[A-Z]", 
                                valuetype = "regex", 
                                case_insensitive = FALSE, 
                                padding = TRUE) |>
                  textstat_collocations(min_count = 100)
fwrite(tstat_col_caps, here::here("content", "project", "tstat_collations_bigram.csv"))

tstat_col2 <- tokens_select(toks_polsent, pattern = "^[A-Z]", 
                                valuetype = "regex", 
                                case_insensitive = FALSE, 
                                padding = TRUE) |> 
              textstat_collocations(min_count = 100, size = 3)
fwrite(tstat_col2, here::here("content", "project", "tstat_collations_trigrams.csv"))
```

## Clustering Based on Article Source

RUN IF WORDS CHANGE

[Source for How to Do This](https://tutorials.quanteda.io/advanced-operations/twitter-user-similarity/)

```{r}
tstat_dist <- as.dist(textstat_dist(dfmat_group_source))
group_clust <- hclust(tstat_dist)

plot(group_clust)

ggdendro::ggdendrogram(group_clust, theme_dendro = FALSE) +
  labs(title = "Cluster Analysis for Article Source",
       x = "Article Sources",
       y = "")
ggsave(here::here("content", "project", "images", "art_source_cluster.png"))
```